### 2017-02-24 Robust-Paper_PLOS_CopyEdit.tex
PLOS copyediting fixups. Added the second tex version with copyedit title and bibliography in main document

% enumerate package lets us use letters instead of numbers
\usepackage{enumerate}

@@

\usepackage{color}

@@

%% Include all macros below
\newcommand{\fixme}[2]{\textsc{\textbf{{#1}: {#2}}}}
\newcommand{\recommend}[1]{\textit{#1}}
\newcommand{\withurl}[2]{{#1}\footnote{\texttt{#2}}}
\newcommand{\rulemajor}[1]{\section*{#1}}
\newcommand{\ruleminor}[1]{\textbf{#1}}
\begin{document}
\vspace*{0.2in}

\begin{flushleft}
{\Large
\textbf\newline{Ten Simple Rules for Making Research Software More Robust}
}
\newline
\\
{Morgan~Taschuk}\textsuperscript{1,\ddag *},
{Greg~Wilson}\textsuperscript{2,\ddag}
\\
\textbf{1} Ontario Institute for Cancer Research / morgan.taschuk@oicr.on.ca
\\
\textbf{2} Software Carpentry Foundation / gvwilson@software-carpentry.org
\\
\bigskip
{\ddag} These authors contributed equally to this work.
\\
* Corresponding author.
\end{flushleft}

@@

Version control is essential to sustainable software development
\cite{wilson2014,wilson2016}.  In particular, developers will struggle
to understand what they have actually built, what it actually does,
and what they have actually released without some mechanical way to
keep track of changes.  They should therefore \ruleminor{put
everything created manually into version control as soon as it is
created}, including programs, original field observations, and the
source files for papers.  Files that can be regenerated at need, such
as the binaries for compiled programs or intermediate files generated
during data analysis, should not be versioned; instead, it is often
more sensible to use an archiving system for them, and store the
metadata describing their contents in version control
instead~\cite{noble2009}.

@@

\emph{S1 Checklist. Robust software checklist.} A checklist summarizing these ten simple rules to apply to your own
software.

@@

>>>>

@@

@@

%% Include all macros below
\newcommand{\fixme}[2]{\textsc{\textbf{{#1}: {#2}}}}
\newcommand{\recommend}[1]{\textit{#1}}
\newcommand{\withurl}[2]{{#1}\footnote{\texttt{#2}}}
\newcommand{\rulemajor}[1]{\section*{#1}}
\newcommand{\ruleminor}[1]{\textbf{#1}}
%% END MACROS SECTION

% enumerate package lets us use letters instead of numbers
\usepackage{enumerate}
\usepackage{color}

\begin{document}
\vspace*{0.2in}

\begin{flushleft}
{\Large
\textbf\newline{Ten Simple Rules for Making Research Software More Robust}
}
\newline
\\
{Morgan~Taschuk}\textsuperscript{1,\ddag *},
{Greg~Wilson}\textsuperscript{2,\ddag}
\\
\bigskip
\textbf{1} Genome Sequence Informatics, Ontario Institute for Cancer Research, Toronto, Ontario, Canada
\\
\textbf{2} Software Carpentry Foundation
\\
\bigskip
{\ddag} These authors contributed equally to this work.
\\
* morgan.taschuk@oicr.on.ca
\end{flushleft}

@@

Version control is essential to sustainable software development
\cite{wilson2014,wilson2016}.  In particular, developers will struggle
to understand what they have actually built, what it actually does,
and what they have actually released without some mechanical way to
keep track of changes.  They should therefore \ruleminor{put
everything into version control as soon as it is
created}, including programs, original field observations, and the
source files for papers.  Files that can be regenerated at need, such
as the binaries for compiled programs or intermediate files generated
during data analysis, should not be versioned; instead, it is often
more sensible to use an archiving system for them, and store the
metadata describing their contents in version control
instead~\cite{noble2009}.

@@

\paragraph*{S1 Checklist.}
\label{S1_Checklist}
{\bf Robust software checklist.} A checklist summarizing these ten simple rules
to apply to your own software.

@@

\bibitem{semver}
Preston-Werner T. Semantic Versioning 2.0.0; 2016.
\newblock \url{http://semver.org/spec/v2.0.0.html}.

### 2017-02-24 robust-checks.tex
PLOS copyediting fixups. Added the second tex version with copyedit title and bibliography in main document

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

@@

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

% enumerate package lets us use letters instead of numbers
\usepackage{enumerate}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace}
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

%% Include all macros below
\newcommand{\fixme}[2]{\textsc{\textbf{{#1}: {#2}}}}
\newcommand{\recommend}[1]{\textit{#1}}
\newcommand{\withurl}[2]{{#1}\footnote{\texttt{#2}}}

@@

\begin{document}
\vspace*{0.2in}

\begin{flushleft}
{\Large
\textbf\newline{Ten Simple Rules for Making Research Software More Robust: The Checklist}
}
\newline
\\
{Morgan~Taschuk}\textsuperscript{1,\ddag *},
{Greg~Wilson}\textsuperscript{2,\ddag}
\\
\textbf{1} Ontario Institute for Cancer Research / morgan.taschuk@oicr.on.ca
\\
\textbf{2} Software Carpentry Foundation / gvwilson@software-carpentry.org
\\
\bigskip
{\ddag} These authors contributed equally to this work.
\\
* Corresponding author.
\end{flushleft}

\begin{easylist}[checklist]
& Use version control.
&& Put everything created manually into version control as soon as it is created.

@@

& Include a small test set that can be run to ensure the software is actually working.
&& Make the test script easy to find and run.
&& Make the test script's output easy to interpret.

>>>>

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=1.0in,footskip=0.75in]{geometry}

@@

% Remove comment for double spacing
\usepackage{setspace}
\onehalfspacing

@@

\begin{document}

\begin{flushleft}
{\Large
\textbf\newline{Ten Simple Rules for Making Research Software More Robust: The Checklist}
}
\end{flushleft}

\begin{easylist}[checklist]
& Use version control.
&& Put everything into version control as soon as it is created.
&& Use a feature branch workflow.

@@

& Include a small test set that can be run to ensure the software is actually working.
&& Make the tests easy to find and run.
&& Make the test script's output easy to interpret.
